Exception Handling Bug Hazards in Android

### 2016-04-13 SPRINGER_JOURNAL/msr_journal.tex
addressing journal reviewers comments on protocol

%Our main goal is to learn from developers about the Java exception handling usage and the main 
%exception handling bug hazards in Android. We therefore use a survey as our main research 
%instrument. The survey mixed  Liket-scale with open-ended questions. The questions were motivated 
%by the analysis of the existing bug hazards detected in the first phase of this study. 
%The next sections detail the survey.

%Our main findings reveal that developers often handle exceptions while developing Android apps and 
%we provide insights into the main challenges faced by them during this task. xxxxxxx

@@

The general research question guiding our exploratory survey is
\emph{RQ 2: How do developers deal with the exception handling code in Android apps and what are the developers' perspectives about the main bug hazards found during the mining study?} This general research question has been broken into a set of research questions that are answered by the exploratory survey.

@@

We used grounded theory coding~\cite{charmaz2006}, iterating through our open-ended survey responses, to answer some of the research questions. The grounded theory coding used in this study consists of two phases: (1) initial coding entailing a close reading of the data and (2) focused coding~\cite{charmaz2006} to pinpoint and develop the most salient themes~\cite{charmaz2006} in the analyzed data. The coding process was performed by two coders who agreed upon the list of themes that emerged from the answer set of each question.

>>>>

%Our main goal is to learn from developers about the Java exception handling usage and the main 
%exception handling bug hazards in Android. We therefore use a survey as our main research 
%instrument. The survey mixed  Liket-scale with open-ended questions. The questions were motivated 
%by the analysis of the existing bug hazards detected in the first phase of this study. 
%The next sections detail the survey.
%Our main findings reveal that developers often handle exceptions while developing Android apps and 
%we provide insights into the main challenges faced by them during this task. xxxxxxx

@@

\textcolor{red}{Hence, the general research question guiding our exploratory survey is twofold \emph{RQ 2: How do developers deal with the exception handling code in Android apps and what are the developers' perspectives about the main bug hazards found during the mining study?} This general research question has been broken into a set of research questions that are answered by the exploratory survey.}

@@

\textcolor{red}{Given the exploratory nature of our research, we used methods from Grounded Theory ~\cite{charmaz2006} to answer some of our research questions by iterating through the open-ended survey responses. The grounded theory coding used in this study consists of at two phases: (1) initial coding entails a close reading of the data and (2) later we used focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes ~\cite{charmaz2006} in the analyzed data. Answers to different questions in the survey were coded separately. For all open-ended questions in the survey, coding was done by two researchers until saturation was reached. Disagreements were discussed and resolved as part of the coding, thus, we are unable to report level of agreement. In all cases, the first author was one of the two coders, and one of the other authors coded the data as well in close collaboration with the first author until saturation was reached. The first author then went through the remaining responses to assign codes to responses.}

%We used grounded theory coding~\cite{charmaz2006}, iterating through our open-ended survey re% sponses, to answer some of the research questions. The 
%grounded theory coding used in this study consists of two phases: (1) initial coding entailing a close reading of the data and (2) focused 
%coding~\cite{charmaz2006} to pinpoint and develop the most salient themes~\cite{charmaz2006} in the analyzed data. The coding process was performed 
%by two coders who agreed upon the list of themes that emerged from the answer set of each question.
